Calculating life expectancy and exploring missingness

### 2017-06-06 Code/1_Explore_Data.Rmd

```{r read_raw_data}
dat <- read.table("./Data/deaths-cause-6913.txt", header = F, sep="\t")
names(dat) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
names(dat) <- c("state.n", "age.n", "sex.n", "race.n", "COD.n", "year.0", "crude.rate", "deaths", "population") 
# names and order of variables in the dataset are noted in the .dic dictionary file found in the same dir as the dataset.
```

@@

dat$stabbrs <- state.abb[match(dat$state, state.name)]
unique(dat$state[is.na(dat$stabbrs)==T]) #Washington DC not defined

dat$stabbrs[dat$state == "Washington DC"] <- "DC"

>>>>

```{r read_raw_data}
dat <- read.table("./Data/deaths-cause-6913.txt", header = F, sep="\t")
#see ./Data/deaths-cause-6913.dic for the data dictionary.

names(dat) <- c("state.n", "age.n", "sex.n", "race.n", "COD.n", "year.0", "crude.rate", "deaths", "population") 
```

@@

dat$stabbrs <- state.abb[match(dat$state, state.name)]
unique(dat$state[is.na(dat$stabbrs)==T]) #Washington DC not defined
dat$stabbrs[dat$state == "Washington DC"] <- "DC"
